---
title: "Reproducible Research with R - Some Quick Overviews"
subtitle: "YMMV"
author: "Roy Mendelssohn"
institute: "Other Worldly"
date: "2019/03/25 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
mono_light(
  base_color = "#23395b",
  link_color = "##ffff88"
)

options(servr.daemon = TRUE)

```


# Overview

- packages

--

- style guidelines

--

- RMarkdown (demystified)

--

- functions and documentation

--

- git and github

--

- pkgdown,  bookdown,  pagedown

---

# Let's Make a Musical!

---

# Let's Make a Package!


---

# Let's Make a Musical Redux!

--

Over a short time period,  Mickey Rooney and Judy Garland made 10 films together

--

No matter what the situation, solution always "let's make a musical"

--

Musical solved all problems.  Baddies vanquished. Judy finds Mickey.  Mickey finds Judy.

--

[Latest Example of Plotline](https://www.youtube.com/watch?v=qkHmUWFFNDc)

---

# inscrutable question "Why"? (a package?) (a duck?)

--
 
Everything loads on a simple command

--

All functions and data immediately available

--

Everything is documented

--

Essential for sending to collaborator or yourself 3 years from now
  
--

See https://swcarpentry.github.io/r-novice-inflammation/08-making-packages-R/


---
# inscrutable question "Why"? (a package?) (a duck?)

Package Reference - http://r-pkgs.had.co.nz

2nd Edition - https://r-pkgs.org

--

[Where we are headed](https://rmendels.github.io/xtractomatic_docs/index.html)

---

# Creating the package (assuming central repository)

--

Create the package, enabling git

--

Use `Github Desktop` to push to Github

--

Else create package, create repository on Github
Clone Repository
Copy files over to cloned repository


---

# An aside about Git

--

Difference between git and Github or Gitlab or Bitbucket

--

Git reference aimed at R - https://happygitwithr.com

--

Git workflows  (more on this at the end)

- https://www.atlassian.com/git/tutorials/comparing-workflows/gitflow-workflow

- https://nvie.com/posts/a-successful-git-branching-model/

---

# Create vignette  (demystifying RMarkdown,  Notebooks, Vignettes)

--

Though can do from GUI,  I prefer command as it creates directory:

```{r create_vignette, echo = TRUE, eval = FALSE}

devtools::use_vignette("my-tracking-package")

```

--

Rmarkdown file, RNotebook, Vignette, Pagedown,  Bookdown

- YAML info at top of file determines what type,  what it can do

--

RMarkdown Cheatsheet  - https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf

From within IDE - https://rmarkdown.rstudio.com/lesson-15.html


---
# Controlling behavior of code chunks

knitr options - https://yihui.name/knitr/options/

--

good practice to name chunks


---

# Coding Guidelines

Stay DRY

--

Think functions,  not scripts

--

follow coding guidelines

--

document functions

--

write tests  (usethis::use_testthat())

--

Package book guidelines - http://r-pkgs.had.co.nz/r.html

tidyverse guidelines - https://style.tidyverse.org

rOpenSci - https://ropensci.github.io/dev_guide/building.html#function-and-argument-naming

---
# One final check

Install package `goodpractice` and run on your package.

https://github.com/MangoTheCat/goodpractice

--

If in Github,  create a README file

devtools::use_readme_rmd()

---
# git worklow

https://www.atlassian.com/git/tutorials/comparing-workflows/gitflow-workflow

https://nvie.com/posts/a-successful-git-branching-model/

Basic idea is work on branches only,  merge into master

Each branch fairly specific, branch name reflects purpose

After merging, if needed branches can be deleted

Formally define versions

Version number system - https://semver.org,

http://r-pkgs.had.co.nz/description.html#version

http://r-pkgs.had.co.nz/release.html




---

